\section{Introduction}
The FLP result~\cite{fischer1985impossibility} showed the impossibility of achieving consensus in an asynchronous
distributed system in the presence of even one failed process. Chandra, Hadzilacos and
Toueg (CHT)~\cite{chandra1996unreliable, chandra1996weakest} in a set of seminal papers showed that this impossibility could
be circumvented using failure detectors, and furthermore that the eventually strong detector ($\Omega$) is the
weakest failure detector required for solving consensus in a distributed system where a majority of processes are
correct. In ``The Weakest Failure Detectors to Solve Certain Fundamental Problems in Distributed
Computing''~\cite{delporte2004weakest}, Delport-Gallet et al. determine the weakest failure detectors required to build
atomic registers, solve consensus, and solve non-blocking atomic commit in any environment, \ie with any number of
failed processes.

Non-blocking atomic commit (NBAC) is a widely studied distributed systems primitive that can be used for transaction
processing in databases~\cite{gray1978notes}. Informally, processeses pariticipating in NBAC start off by proposing a
binary YES (the process can commit a transaction) or NO (the process cannot commit a transaction) value, and eventually
all processes must decide between commiting the transaction (\ie YES), or aborting (\ie NO). A decision to commit
requires that all processes have voted YES, while the algorithm can decide to abort either because one or more of the
processes voted NO, or a failure was detected. Furthermore, to eliminate some vacuous solutions, in the absense of
failures, if all processes vote YES, the final decisions must be to commit. NBAC is provably harder than consensus,
Guerraoui~\cite{guerraoui1995revisiting} showed that  NBAC
cannot be solved in an aynchronous distributed system with a single failure, even when an unreliable failure detector is
used. While prior work~\cite{guerraoui2002weakest} had looked at failure detectors needed to solve NBAC in some specific
environments, it was unknown if there was a weakest failure detector to solve NBAC in any environment.

Consensus is similarly an important, and widely studied distributed systems primitive. While the CHT result requires
that a majority of processes be correct, a result from Lo et al.~\cite{lo1994using} shows that in a shared-memory system
$\Omega$ can be used to solve consensus in all environments. This paper bridges the gap between these results,
and determines the weakest failure detector to solve consensus in all environments in a message-passing system.

\textbf{Outline} In this paper we use the same model for asynchronous distributed systems with failure detectors used
by~\cite{chandra1996unreliable, chandra1996weakest}. We start by reiterating the main points of that model, before
delving into the actual results, proofs, and possible future work.

